%!TEX encoding = UTF8
%!TEX root = resume.tex

\begin{rubric}{Experience}

\subrubric{Research Experience}

\entry*[01/2016 \-- 08/2023] \position{Binghamton University, Computer Science Department}{Binghamton, NY}{Research Assistant}
\par \begin{list1}
	\item Repurposed Intel Memory Protection Extensions for generalized storage, and implemented analyses for the LLVM compiler toolchain to replace memory accesses with these inlined register operations.
	\item Engineered an implementation of the RISC-V architecture employing inline code tagging for integrity models from compiler-driven static program analysis techniques, using the LLVM compiler toolchain.
	\item Extended our implementation of the RISC-V architecture and LLVM compiler toolchain to perform out-of-band data tagging, with the ability to achieve relaxation and linkage resolution at link-time using a modified version of the LLD linker.
	\item Developed a prototype extending data tagging for a read- and write-limited data model that specifically enforces compile-time \texttt{const} qualifiers as run-time assurances.
	\item Developed a technique for extracting design patterns from C++ source code and encoding as a finite state machine with an XML machine-readable representation.
	\item Researched scientific utilization of performance benchmark tools for the computer security domain.
\end{list1}
%%%%
\entry*[05/2004 \-- 08/2004] \position{United States Naval Research Laboratory}{Washington, DC}{Networks and Communications Systems Intern}
\par \begin{list1}
		\item Prototyped a Java Management Extension (JMX) for Mobile Ad Hoc Wireless Networks (MANETs) serving city-sized distributed sensor networks in real-time.
	\end{list1}

\subrubric{Professional Experience}

\entry*[01/2022 \-- Present] \position{Binghamton University, Computer Science Department}{Binghamton, NY}{Lecturer}
\par \begin{list2}%
	\item {Fall 2023 \--- CS 580U: Programming Systems and Tools}
	\item {Fall 2022 \--- CS 580U: Programming Systems and Tools}
	\item {Spring 2022 \--- CS 458, CS 558: Introduction to Computer Security}
\end{list2}
%%%%
\entry*[08/2017 \-- 05/2023] \position{Binghamton University, Computer Science Department}{Binghamton, NY}{Teaching Assistant}
\par \begin{list2}%
	\item {Spring 2023 \--- CS 458, CS 558: Introduction to Computer Security}
	\item {Spring 2018 \--- CS 480, CS 580: Special Topics: Software Security}
	\item {Fall 2017 \--- CS 220: Computer Systems II, Architecture and C Programming}
\end{list2}
%%%%
\entry*[09/2011 \-- 06/2014] \position{United States Navy, Trident Training Facility}{Silverdale, WA}{Instructor}
\par \begin{list1}
	\item Qualified as Instructor, Instructor Evaluator and Course Supervisor. Served as Navigation Department Director, managing a department of 40 instructors and 11 labs. Awarded Navy and Marine Corps Commendation Medal with Gold Star.
	\item Improved annual throughput in a ship piloting simulator by 18\% (75 sessions) by repairing over 30 script files and qualifying two new instructors. Created an additional 32 trainer sessions per month by guiding a comprehensive lab redesign.
	\item Delivered lectures for 120 submarine officers annually (66\% increase) and practical skills training for 23 ships, earning a ``highly effective'' rating by external auditors.
%	\item Cut exam grading and test item analysis time in half (8 hours/graduating class) by building an automated evaluation tool.
\end{list1}
%%%%
\entry*[04/2010 \-- 04/2011] \position{Headquarters, U.S. Forces Afghanistan}{Kabul, AF}{Operations Officer}
\begin{list2}
	\item Guided ad-hoc, cross-functional teams of 6-8 in a position normally assigned to a more senior pay grade. Awarded Defense Meritorious Service Medal.
	%	\item Edited daily operations summaries for military and diplomatic leadership. Authored logistical, manpower and operational orders for the Commanding General.
	\item One of three officers selected from a theatre-level command to certify deployment readiness for 54 units and 6500+ personnel.
	\item Expedited processing by 30\% (4 days) and enabled a 144\% increase (128 items) in annual traffic by improving tracking methods, reducing retention requirements and implementing SharePoint collaboration tools.
	\item Responded to a major diplomatic cables leak by building a database for tracking compromised personnel that reduced outgoing traffic by 92\% (920 messages).
\end{list2}
%%%%
\entry*[08/2009 \-- 08/2011] \position{United States Navy, Amphibious Squadron Six}{Little Creek, VA}{Department Head}
\begin{list2}
	\item Qualified as Staff Tactical Watch Officer (operations floor manager). Served as Administrative Department Head with 6 direct reports and oversight of 4 ships' administrative and human resources departments. Awarded Navy and Marine Corps Commendation Medal.
	%	\item Led a team responsible for 4 ships and embarked aviation, construction and medical assets.
	\item Authored contingency plans and coordinated with 8 partner nations to deliver over 100K pounds of humanitarian supplies following the 2010 Haitian earthquake.
	%	\item Increased staff flexibility and capabilities by volunteering to attend 3 operational planning schools outside normal job responsibilities.
	%	\item Became a self-taught expert in military human resources programs in support of a major command staff, 2 flagships and 6 assigned subordinate ships.
	%	\item Improved morale by correcting errors of 9 awards, 25 performance evaluations, and 5 pay and benefits actions within 6 months of arrival.
	%	\item Enhanced deployment readiness and staff integration by revitalizing 2 neglected personnel programs.
\end{list2}
%%%%
\entry*[12/2006 \-- 06/2009] \position{United States Navy, USS Maine (SSBN-741)}{Silverdale, WA}{Division Officer}
\begin{list2}
	\item Qualified as Submarine Warfare Officer and Nuclear Engineering Officer. Awarded Navy and Marine Corps Achievement Medal.
	%	\item Produced near-term schedules for executive leadership and managed 2 divisions responsible for navigation and communication systems.
	\item Held responsibility as the Commanding Officer's direct representative for a \$2B submarine, \$100M nuclear reactor plant and \$50M-\$75M annual operating budgets.
	%	\item Selected as the ship’s nuclear weapons courier out of a group of 10 officers for exceptional attention to detail.
	%	\item Authored and validated 2 operational risk management plans for navigating in dense shipping areas.
	%	\item Coordinated entry, maintenance and quality assurance retesting for all ballast control tanks and associated control systems ahead of schedule during a major maintenance refit.
	\item Guided operation, maintenance and testing of nuclear reactor instrumentation, control systems and protective features. Resolved a decade-long persistent fault in the S8G Nuclear Instrumentation and Pump Control systems.
	%	\item Managed a division of 8 to complete all operator qualifications before required and inspired 4 to achieve additional advanced supervisory qualifications.
\end{list2}
\end{rubric}
